Shallow EDSLs and Object-Oriented Programming

### 2016-06-20 paper/sections/Introduction.tex
Revised Section 2
Latest

Although the above definition is quite reasonable and widely accepted,
it leaves some space to (mis)interpretation. For example it is unclear 
how to classify an EDSL implemented using the {\sc Composite} or {\sc Interpreter} 
patterns in OOP. Would this OO approach be
classified as a shallow or deep embedding? We believe arguments can be
made both ways. Since the {\sc Composite} or {\sc Interpreter}
patterns are normally accepted to provide a way to encode ASTs, it would be
reasonable to say that \emph{according to definition of deep embedding
  above, the OO approach classifies as a deep
  embedding}. However, as we shall argure in the remainder of the
paper, another possible interpretation is that the OO approach is
really a shallow embedding. At least some authors~\cite{} seem to
implicitly agree with 
the latter interpretation.

@@

>>>>

Although the above definition is quite reasonable and widely accepted,
it leaves some space to (mis)interpretation. For example it is unclear 
how to classify an EDSL implemented using the {\sc Composite} or {\sc Interpreter} 
patterns in OOP. Would this OO approach be
classified as a shallow or deep embedding? We believe arguments can be
made both ways. Since the {\sc Composite} or {\sc Interpreter}
patterns are normally accepted to provide a way to encode ASTs, it would be
reasonable to say that \emph{according to definition of deep embedding
  above, the OO approach classifies as a deep
  embedding}. However, as we shall argue in the remainder of the
paper, another possible interpretation is that the OO approach is
really a shallow embedding. At least some authors~\cite{} seem to
implicitly agree with 
the latter interpretation.

@@

\item {Identifying Advantages of OOP languages for Shallow Embeddings:}
